Model Checking

### 2023-09-05 owen/Write Ups/03_existing_models.qmd
add quick version for fitting model to permuted data

>>>>

### Robustness to Correlation

A valid concern here is the large correlation between the data used at
each step. For example, when using the previous 10 games as the history,
subsequent games will use an average with 9 of the 10 terms in the average being
identical. This leads to severe correlation.

One potential way to deal with this (mentioned by the authors of the Deng et al 
paper) is to test for this effect. One way to do this would be to consider
a permutation test. The results can be randomly permuted, which allows the
construction of an empirical set of estimates under the permutation.
This would need to be considered for this data also.
